Lesson 5
========================================================

### Multivariate Data
Notes:

***

### Moira Perceived Audience Size Colored by Age
Notes:

***

### Third Qualitative Variable
Notes:

```{r Third Qualitative Variable}
library(ggplot2)

pf <- read.csv('pseudo_facebook.tsv', sep = '\t')

ggplot(aes(x = gender, y = age), data = subset(pf, !is.na(gender))) + geom_boxplot() +
  stat_summary(fun.y = mean, geom = 'point', shape = 4)

ggplot(aes(x = age , y=friend_count), data=subset(pf, !is.na(gender))) + 
  geom_line(aes(color=gender), stat='summary', fun.y = mean)
```

***

# Write code to create a new data frame,
# called 'pf.fc_by_age_gender', that contains
# information on each age AND gender group.

# The data frame should contain the following variables:

#    mean_friend_count,
#    median_friend_count,
#    n (the number of users in each age and gender grouping)

# Here is an example of the structure of your data frame. Your
# data values will be different. Note that if you are grouping by
# more than one variable, you will probably need to call the
# ungroup() function. 

#   age gender mean_friend_count median_friend_count    n
# 1  13 female          247.2953                 150  207
# 2  13   male          184.2342                  61  265
# 3  14 female          329.1938                 245  834
# 4  14   male          157.1204                  88 1201

```{r}
pf.fc_by_age_gender <- pf %>%
  filter(!is.na(gender)) %>%
  group_by(age, gender) %>%
  summarise(mean_friend_count = mean(friend_count),
            median_friend_count = median(friend_count),
            n=n()) %>%
  ungroup() %>%
  arrange(age,gender)

head(pf.fc_by_age_gender)
```

### Plotting Conditional Summaries
Notes:

```{r Plotting Conditional Summaries}

ggplot(data=pf.fc_by_age_gender, aes(x=age, y=median_friend_count, color=gender)) + geom_line()
```

***

### Thinking in Ratios
Notes:

***

### Wide and Long Format
Notes:

***

### Reshaping Data
Notes:

```{r}
#install.packages('reshape2')
library(reshape2)

# dcast : result as dataFrame
pf.fc_by_age_gender.wide <- dcast(pf.fc_by_age_gender,
                                  age ~ gender,
                                  value.var = 'median_friend_count')
head(pf.fc_by_age_gender.wide)

# The linetype parameter can take the values 0-6:
# 0 = blank, 1 = solid, 2 = dashed
# 3 = dotted, 4 = dotdash, 5 = longdash
# 6 = twodash

```


***
# Plot the ratio of the female to male median
# friend counts using the data frame
# pf.fc_by_age_gender.wide.
### Ratio Plot
Notes:

```{r Ratio Plot}
ggplot(data=pf.fc_by_age_gender.wide, aes(x=age, y=female/male)) + geom_line() +
  geom_hline(yintercept = 1, alpha = 0.3, linetype = 2)
```

***

### Third Quantitative Variable
Notes:

```{r Third Quantitative Variable}

```

***

### Cut a Variable
Notes:

```{r Cut a Variable}

```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}

```

***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}

```

***

### Friending Rate
Notes:

```{r Friending Rate}

```

***

### Friendships Initiated
Notes:

What is the median friend rate?

What is the maximum friend rate?

```{r Friendships Initiated}

```

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

```

***

### Sean's NFL Fan Sentiment Study
Notes:

***

### Introducing the Yogurt Data Set
Notes:

***

### Histograms Revisited
Notes:

```{r Histograms Revisited}

```

***

### Number of Purchases
Notes:

```{r Number of Purchases}

```

***

### Prices over Time
Notes:

```{r Prices over Time}

```

***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}

```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:

***

### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

